---
title: "Tidymodels Organic Project"
output: html_notebook
---


## Load Libraries 

```{r, warning=FALSE, message=FALSE}

library(C50)
library(caret)
library(tidyverse)
library(tidymodels)
library(janitor)
library(skimr)
library(kableExtra)
library(GGally)
library(kableExtra) # -- make nice looking resutls when we knitt 
library(vip)        # --  tidymodels variable importance
library(fastshap)   # -- shapley values for variable importance 
library(MASS)
library(rpart.plot) # -- plotting decision trees 
library(imputeMissings)
```

## Load Data

Import your data with read_csv()

```{r}
odat1 <- read_csv("organics.csv") %>%
  clean_names()

# remove "rejected" variables from the data frame

odat = subset(odat1, select= -c(id, dem_cluster, target_amt))
head(odat)

```

## chage target to factor and Profile data


```{r}

odat$target_buy <- as.factor(odat$target_buy)

odat %>%
  skim()

```
```{r}

odat2 <- impute(odat)
odat2 %>%
    skim()
```



## Partition your data 70/30 (train / test split) 


```{r}
# -- set a random seed for repeatablity 
set.seed(43)

# -- performs our train / test split 
odat_split <- initial_split(odat, prop = 0.7)

# -- extract the training data 
odat_train <- training(odat_split)
# -- extract the test data 
odat_test <- testing(odat_split)

sprintf("Train PCT : %1.2f%%", nrow(odat_train)/ nrow(odat) * 100)
sprintf("Test  PCT : %1.2f%%", nrow(odat_test)/ nrow(odat) * 100)

head(odat_train)

```


## Recipe 
```{r}
odat_recipe <- recipe(target_buy ~ ., data = odat) %>%
  #step_dummy(all_nominal(), -all_outcomes()) %>%
  step_modeimpute(all_nominal(), -all_outcomes()) %>%
  step_medianimpute(all_numeric()) %>%
  #step_naomit() %>%
    prep()

odat_recipe
```

## Bake the prediction 
```{r}
bake_train <- bake(odat_recipe, new_data = odat_train)
bake_test  <- bake(odat_recipe, new_data = odat_test)
```


## Fit a logistic model

```{r}
logistic_glm <-logistic_reg(mode = "classification") %>%
                  set_engine("glm") %>%
                  fit(target_buy ~ ., data = bake_train)

## -- check out your parameter estimates ... 
tidy(logistic_glm) %>%
  mutate_at(c("estimate", "std.error", "statistic", "p.value"),round, 4)

```



## Stepwise logistic

```{r}

steplog <- glm(target_buy ~ ., data = bake_train, family=binomial(link="logit"))
step <- stepAIC(steplog, direction="both")
summary(step)

```
```{r}

stepwise_glm <-logistic_reg(mode = "classification") %>%
                  set_engine("glm") %>%
                  fit(target_buy ~ dem_affl + dem_age + dem_gender, data = bake_train)

tidy(stepwise_glm) %>%
  mutate_at(c("estimate", "std.error", "statistic", "p.value"),round, 4)

```


## Fit a tree model 

```{r}
odat_tree <- decision_tree(mode="classification") %>%
                  set_engine("rpart") %>%
                  fit(target_buy ~ ., data = odat_train)


odat_tree$fit

options(scipen=0)
rpart.plot(odat_tree$fit, roundint=FALSE, extra = 3)

```


## Tuning the cost complexity parameter
```{r}

set.seed(123)
treemod <- train(
                  target_buy ~ dem_cluster_group + dem_gender + dem_reg + dem_tv_reg + prom_class+ 
                  dem_affl + dem_age + prom_spend + prom_time, 
                  data = odat2, 
                  method="rpart",
                  trControl = trainControl("cv", number = 10),
                  tuneLength = 
                  )

#Plot model accuracy vs different values of cp (complexity parameter)
plot(treemod)
treemod$bestTune

```

### -  try a diff tree 
```{r}
odat_tree2 <- decision_tree(mode="classification",
                            cost_complexity = 0.0008,
                            tree_depth = 5,
                            min_n = 2) %>%
                  set_engine("rpart") %>%
                  fit(target_buy ~ ., data=odat_train)

odat_tree2$fit

options(scipen = 0)
  
rpart.plot(odat_tree2$fit, roundint=FALSE, extra=3)

```
## try C5.0 
```{r}
odat_tree_c50 <- decision_tree(mode="classification") %>%
                  set_engine("C5.0") %>%
                  fit(target_buy ~ ., data=odat_train)

odat_tree2$fit

```
##try C5.0 in basic R code 
```{r}
vars <- c( "dem_cluster_group", "dem_gender", "dem_reg","dem_tv_reg", "prom_class",
                  "dem_affl", "dem_age", "prom_spend","prom_time")

c5_tree <- C5.0(x = odat_train[,vars], y = odat_train$target_buy)

summary(c5_tree)
plot(c5_tree)


```


## Prep for Evaluation (logistic)


```{r}

# -- training 
predict(logistic_glm, bake_train, type = "prob") %>%
  bind_cols(.,predict(logistic_glm, bake_train)) %>%
  bind_cols(.,bake_train) -> scored_train_glm

head(scored_train_glm)

# -- testing 
predict(logistic_glm, bake_test, type = "prob") %>%
  bind_cols(.,predict(logistic_glm, bake_test)) %>%
  bind_cols(.,bake_test) -> scored_test_glm

head(scored_test_glm)


```

## Evaluate


```{r}

# -- AUC: Train and Test 
scored_train_glm %>% 
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part="training") %>%
  bind_rows( scored_test_glm %>% 
               metrics(target_buy, .pred_1, estimate = .pred_class) %>%
               mutate(part="testing") 
  ) 
  


# -- Variable Importance top 10 features  
logistic_glm %>%
  vip(num_features = 5)

# -- ROC Charts 
options(yardstick.event_first = FALSE) #reverse roc 
scored_train_glm %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_glm %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()


# -- Confustion Matricies  
scored_train_glm %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Train Confusion Matrix")

scored_test_glm %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Test Confusion Matrix")




```
## Prep for Evaluation (logistic stepwise)


```{r}

# -- training 
predict(stepwise_glm, bake_train, type = "prob") %>%
  bind_cols(.,predict(stepwise_glm, bake_train)) %>%
  bind_cols(.,bake_train) -> scored_train_stepwise

head(scored_train_stepwise)

# -- testing 
predict(stepwise_glm, bake_test, type = "prob") %>%
  bind_cols(.,predict(stepwise_glm, bake_test)) %>%
  bind_cols(.,bake_test) -> scored_test_stepwise

head(scored_test_stepwise)



```

## Evaluate


```{r}

# -- AUC: Train and Test 
scored_train_stepwise %>% 
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part="training") %>%
  bind_rows( scored_test_stepwise %>% 
               metrics(target_buy, .pred_1, estimate = .pred_class) %>%
               mutate(part="testing") 
  ) 
  


# -- Variable Importance top 10 features  
stepwise_glm %>%
  vip(num_features = 5)

# -- ROC Charts 
options(yardstick.event_first = FALSE) #reverse roc 
scored_train_stepwise %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_stepwise %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()


# -- Confustion Matricies  
scored_train_stepwise %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Train Confusion Matrix")

scored_test_stepwise %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Test Confusion Matrix")




```



## Prep for Evaluation (odat tree)


```{r}

# -- training 
predict(odat_tree, odat_train, type = "prob") %>%
  bind_cols(.,predict(odat_tree, odat_train)) %>%
  bind_cols(.,odat_train) -> scored_train_tree

head(scored_train_tree)

# -- testing 
predict(odat_tree, odat_test, type = "prob") %>%
  bind_cols(.,predict(odat_tree, odat_test)) %>%
  bind_cols(.,odat_test) -> scored_test_tree

head(scored_test_tree)
```

## Evaluate


```{r}

# -- AUC: Train and Test 
scored_train_tree %>% 
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part="training") %>%
  bind_rows( scored_test_tree %>% 
               metrics(target_buy, .pred_1, estimate = .pred_class) %>%
               mutate(part="testing") 
  ) 
  


# -- Variable Importance top 10 features  
odat_tree %>%
  vip(num_features = 5)

# -- ROC Charts 
scored_train_tree %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_tree %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()


# -- Confustion Matricies  
scored_train_tree %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Train Confusion Matrix")

scored_test_tree %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Test Confusion Matrix")




```


## Prep for Evaluation (odat tree2)


```{r}

# -- training 
predict(odat_tree2, odat_train, type = "prob") %>%
  bind_cols(.,predict(odat_tree2, odat_train)) %>%
  bind_cols(.,odat_train) -> scored_train_tree2

head(scored_train_tree2)

# -- testing 
predict(odat_tree2, odat_test, type = "prob") %>%
  bind_cols(.,predict(odat_tree2, odat_test)) %>%
  bind_cols(.,odat_test) -> scored_test_tree2

head(scored_test_tree2)
```

## Evaluate


```{r}

# -- AUC: Train and Test 
scored_train_tree2 %>% 
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part="training") %>%
  bind_rows( scored_test_tree2 %>% 
               metrics(target_buy, .pred_1, estimate = .pred_class) %>%
               mutate(part="testing") 
  ) 
  


# -- Variable Importance top 10 features  
odat_tree2 %>%
  vip(num_features = 5)

# -- ROC Charts 
scored_train_tree2 %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_tree2 %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()


# -- Confustion Matricies  
scored_train_tree2 %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Train Confusion Matrix")

scored_test_tree2 %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Test Confusion Matrix")




```

## Prep for Evaluation (odat C5.0)


```{r}

# -- training 
predict(odat_tree_c50, bake_train, type = "prob") %>%
  bind_cols(.,predict(odat_tree_c50, bake_train)) %>%
  bind_cols(.,bake_train) -> scored_train_tree_c50

head(scored_train_tree_c50)

# -- testing 
predict(odat_tree_c50, bake_test, type = "prob") %>%
  bind_cols(.,predict(odat_tree2, bake_test)) %>%
  bind_cols(.,bake_test) -> scored_test_tree_c50

head(scored_test_tree_c50)
```

## Evaluate


```{r}

# -- AUC: Train and Test 
scored_train_tree_c50 %>% 
  metrics(target_buy, .pred_1, estimate = .pred_class) %>%
  mutate(part="training") %>%
  bind_rows( scored_test_tree2 %>% 
               metrics(target_buy, .pred_1, estimate = .pred_class) %>%
               mutate(part="testing") 
  ) 
  


# -- Variable Importance top 10 features  
odat_tree_c50 %>%
  vip(num_features = 5)

# -- ROC Charts 
scored_train_tree_c50 %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_tree2 %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(target_buy, .pred_1) %>%
  autoplot()


# -- Confustion Matricies  
scored_train_tree_c50 %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Train Confusion Matrix")

scored_test_tree_c50 %>%
  conf_mat(target_buy, .pred_class) %>%
  autoplot( type = "heatmap") +
  labs(title="Test Confusion Matrix")




```



## Load Holdout Data

Import your data with read_csv()

```{r}
new_odat1 <- read_csv("New_organics.csv") %>%
  clean_names()

# remove "rejected" variables from the data frame

new_odat = subset(new_odat1, select= -c(id, dem_cluster))
head(new_odat)


```

```{r}

new_odat <- impute(new_odat)
new_odat %>%
    skim()
```

## Bake
```{r}
bake_holdout <- bake(odat_recipe, new_data = new_odat)
```

## Apply model 


```{r}

predict(odat_tree2, new_odat, type = "prob") %>%
  bind_cols(.,predict(odat_tree2, new_odat)) %>%
  bind_cols(.,new_odat) -> scored_train_tree_new

head(scored_train_tree_new)

```
```{r}
write.csv(scored_train_tree_new,"scored_train_tree_new.csv")
```

